### 2021-09-03 README.Rmd
update readme

1. open the `.Rproj` file in RStudio      
2. run `renv::restore()` to download and install the packages required to run our code     
3. run `targets::tar_make()` to run our code in order, the final step of this will be 
 knitting the R Markdown document to produce the `paper.docx`

>>>>

1. open the `.Rproj` file in RStudio      
2. run `renv::restore()` to download and install the packages required to run our code     
3. run `targets::tar_make()` to run our analysis R code in the `analysis` directory in order, the final step of this will be 
 knitting the R Markdown document to produce our submitted manuscript, `paper.docx`
